\documentclass[a4paper,12pt]{letter}  % Use letter class
\usepackage[left=2.5cm, right=2.5cm, top=2.5cm, bottom=2.5cm]{geometry}  % Adjust margins

\begin{document}

% Sender's Information
\signature{Mukhtar M. Lawan}  % Signature at the end
\address{Mukhtar M. Lawan \\ Rehrstieg 16D \\ 21147, Hamburg \\ 
}

% Recipient's Information
\begin{letter}{Freiheit.com, \\ Budapester Str. 45 \\ 20359 Hamburg \\ Germany}


\opening{Dear Freiheit.com team,}

\begin{center}
    \textbf{Application for Software Engineer Position}
\end{center}

I am excited to apply for the position of Software Engineer at Freiheit. Having
recently completely my PhD in Theoretical and Computational Physics, I am eager to 
transition into the field of professional software development and engineering where
I can apply my strong analytical thinking, data analysis, and coding skills to tackle 
complex challenges. I am particularly drawn to Freiheit's innovative approach and agile
development culture, which resonated with my passion for working in a vibrant, collaborative
team with a positive spirit.


I garnered my mathematical and coding skills from studying during my masters 
at the African University of science and Technology (AUST)-one of the 12 African Centers
of Excellence- I was selected for an elite program, where I was one of the only 15 
scholars chosen from across Africa. This experience strenghtened my ability to learn
new methodologies and paradigms, a skill which I carried into my PhD at the Max planck
Institute for Structure and Dynamics of Matter (MPSD) in Hamburg under the  prestigious 
Marie Skłodowska-Curie Action (MSCA Horizon 2020) fellowship. 

During my PhD, I worked in developing Computational models and analyzing large datasets.
I took full ownership of my reseach projects, self-organizing my work and ensuring timely completion 
of deliverables—an essential quality in agile development environments.

With a solid background in Physics and  Mathematics, sofware development and problem-solving, I am 
eager to bring my expertise to Freiheit and contribute impactful solutions. 

I look forward to discuss the opportunity and how my skills and background align with
your team goals. 

Thank you for your time and considerations.

Yours Sincerely, \\
\vspace{5mm}
Dr. Mukhtar M. Lawan

\closing{\hspace*{0pt}Best regards, }

% End Letter
\end{letter}

\end{document}
